\todo{Something} presents OpenAdcess

### 2017-02-09 paper-sponsorships.tex
Ad enhanced fonts and native ads

\subsection{Ad Enhanced Fonts}
\todo{Computer modern replaced with characters replaced by logos}

\subsection{Native Ads}
\todo{Content that seems like research but is actually an ad}

\subsection{Branded mathematical objects}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

>>>>

\subsection{Ad Enhanced Fonts}
Computer Modern is a staple of modern papers, but we believe that this font can
be monetized.
By replacing the characters in the default latex with logos of companies we can
convey the same information in an ad enhanced way.

During each Call for Papers we will also put out a simultaneous Call for
Logos during which companies bid on which letter they want.
We require that the company logo is a stylized version of the letter being
replaced to avoid a Wingdings situation \todo{Cite NYC controversy}.

\subsection{Native Ads}
\todo{Define native advertising}

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads are to be native, an advertisement that is recognizable as an ad
will result in a strong reject of the paper.
The ad section must be at least one page long, but there is upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

\subsection{Investor Author Dispute Settlement}
We have founded an Investor Author Dispute Settlement (IADS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle will dash the hopes of the typical \todo{brand}
consumer.
Moreover, since \todo{brand} owns both of these complexity classes as defined
in section \todo{ref branded objects section} their assets will lose value and
this loss must be compensated by the ``bloggers".

% TODO: Reference this:
% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
\subsection{Branded mathematical objects}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.
